Automatic Code Cleaning in R with `Rclean`

### 2020-03-12 ropensci/rclean_technote.Rmd
Increases figure resolution

Data analysis can be messy and complicated, so it's no wonder that the
code often reflects this. "What did I measure? What analyses are
relevant to them? Do I need to transform the data? What's the function
for the analysis I want to run?" In addition, although many
researchers see the value in learning to write software, the entry
level is still exceedingly high. The `R` language has become very
popular among scientists and analysts because of the lower threshold,
which is good in that it empowers science. The downside is that
learning to create good software is a skill that takes a considerable
amount of time to learn, which means that many scientists write code
that will get the job "done" but lacks transparency and is highly
unstable (i.e. buggy).

@@

```{R prov-graph, fig.cap = "Network diagram of the prospective data provenance generated for an example script. Arrows indicate which lines of code (numbered) produced which objects (named).", echo = FALSE}

@@

```{R ex-code_graph, fig.cap = "Example of the plot produced by the code_graph function showing which lines of code produce which variables and which variables are used by other lines of code."}

>>>>

Data analysis can be messy and complicated. Because of project
complexities and time contraints, analytial software often reflects
these challenges. "What did I measure? What analyses are relevant to
them? Do I need to transform the data? What's the function for the
analysis I want to run?" In addition, although many researchers see
the value in learning to write software, the entry level is still
exceedingly high. The `R` language has become very popular among
scientists and analysts because of the lower threshold, which is good
in that it empowers science. The downside is that learning to create
good software is a skill that takes a considerable amount of time to
learn, which means that many scientists write code that will get the
job "done" but lacks transparency and is highly unstable (i.e. buggy).

@@

```{R prov-graph, dpi = 300, fig.cap = "Network diagram of the prospective data provenance generated for an example script. Arrows indicate which lines of code (numbered) produced which objects (named).", echo = FALSE}

@@

```{R ex-code_graph, dpi = 300, fig.cap = "Example of the plot produced by the code_graph function showing which lines of code produce which variables and which variables are used by other lines of code."}
